Paper Title*\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-07-16 paper.tex
Updates from Overleaf

\section{Our Method}

\color{red}
\centering
\textbf{\textit{MAYBE}}
\color{black}

\section{Experiments}

@@

\begin{thebibliography}{00}
\end{thebibliography}

>>>>

\section{Method}

An ensemble of VGG-16s were employed and evaluated to classify fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.

% In this work we intended to employ and evaluate a CNN architecture capable of detecting the presence or not of falls in videos, thus approaching the problem as a binary classification. To this end, we select the CNN architecture VGG16, since it is well known, and yields satisfactory results. Furthermore, based on the results of Wang et al.~\cite{wang2015towards}, in which a multi-streamed CNN outperformed single-stream ones, a ensembled was also exerted to learn the influence of three selected streams, each stream fed with a hand-crafted feature, them being: (i) optical flow, (ii) rgb, and (iii) saliency map.

\subsection{Transfer Learning}

The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses a relatively small amount of human fall samples in their videos, which would limit the CNNs learning capabilities to detect a fall event. Thus, the need to transfer learning from other datasets.

The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset, and later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset. The reasoning being that the network would initially learn low level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.

The 14 initial layer's weights were then frozen, and the last two fully connected layers were separately fine-tuned, with dropout regularization, over the extracted hand-crafted features of the URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised} datasets. This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.

\subsection{Hand-crafted Features}

stacking MAYBE

\subsection{Classification}

svm

\section{Experiments}
\label{sec:experiments}

@@

%\begin{thebibliography}{00}
%\end{thebibliography}

\bibliographystyle{IEEEtran}
\bibliography{paper}
